# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r}
activity<-read.csv("activity//activity.csv")

steps_per_day <- aggregate(steps ~ date, activity, sum)
```

## What is mean total number of steps taken per day?
```{r}
hist(steps_per_day$steps,15)
abline(v=median(steps_per_day$steps),col="blue")
abline(v=mean(steps_per_day$steps),col="red")
legend("topright", lty=c(1,1), col = c("red","blue" ), legend = c( paste(c("Mean:",format(mean(steps_per_day$steps),nsmall=2)), collapse = " "), paste("Median: ",median(steps_per_day$steps))))
```
#### Mean and Mode (are present on the histogram)
```{r}
mean(steps_per_day$steps)
median(steps_per_day$steps)


```


## What is the average daily activity pattern?

```{r}
##average steps per 5 minutes intervals
stepmean<-aggregate(activity$steps, list(activity$interval), mean, na.rm=T)
names(stepmean)<-c("interval", "steps")
plot(stepmean$interval, stepmean$steps, type="l")


##interval contains the maximum number of steps:
stepmean[order(stepmean$steps),][ length(stepmean$steps),]$interval

```





## Imputing missing values
#### Count of NA rows
```{r}
sum(is.na(activity))
```

#### Replacement of the NA by the mean of the corres[ponding interval
```{r}
activity <- merge(activity, stepmean, by="interval", suffixes=c("",".y"))
naindexes <- is.na(activity$steps)
activity$steps[naindexes] <- activity$steps.y[naindexes]
activity <- activity[,c(1:3)]
```
#### Histogram of the repared data
```{r}
steps_per_day <- aggregate(steps ~ date, activity, sum)
hist(steps_per_day$steps,15)
abline(v=median(steps_per_day$steps),col="blue")
abline(v=mean(steps_per_day$steps),col="red")
legend("topright", lty=c(1,1), col = c("red","blue" ), legend = c( paste(c("Mean:",format(mean(steps_per_day$steps),nsmall=2)), collapse = " "), paste("Median: ",format(median(steps_per_day$steps),nsmall=2))))
```
#### Median has been moved to the mean value

## Are there differences in activity patterns between weekdays and weekends?

#### Convering date to Date format
```{r}
activity$date<-as.Date(activity$date)
```

#### function to parse the dates
```{r}
parsedate <- function(date) {
     if (weekdays(date) %in% c("Saturday", "Sunday")) {
         "weekend"
     } else {
         "weekday"
     }
 }

#### add the new property
activity$day <- as.factor(sapply(activity$date, parsedate))

```